---
title: "P8105_hw6_yw3774"
author: "Yida Wang"
date: "11/24/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(modelr)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
# Problem 1

### Data cleaning
```{r}
birthweight = read_csv("birthweight.csv") %>%
  janitor::clean_names() %>% 
  mutate(
    babysex = ifelse(babysex == 1, "male", "female"),
    babysex = as.factor(babysex),
    frace = factor(recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown")), 
    mrace = factor(recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other")),
    malform = ifelse(malform == 0, "absent", "present"), 
    malform = as.factor(malform)
  )
```

### Check missing value 
```{r}
purrr::map(birthweight, ~sum(is.na(.)))
```

### Build the model base on a data-driven model-building process

Step-wise regression
```{r}
mult.fit = lm(bwt ~ ., data = birthweight)
step(mult.fit, direction = 'both')
```
According to the result calculating above, the regression model of birthweight contains babysexmale, bhead, blength, delwt, fincome, gaweeks, mheight, mraceBlack, mracePuerto Rican, mraceWhite, parity, ppwt, smoken.
```{r}
model_1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)
```

### Residuals plot

```{r}
birthweight %>% 
  add_predictions(model_1) %>% 
  add_residuals(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.3) + 
  geom_smooth(se = F, color = "red", method = "lm") +
  labs(title = "Fitted Values vs Residuals of the Model",
       x = "Fitted value", 
       y = "Residual")
```
It shows that most of the points are symmetrically distributed and clustered around 0 on the y-axis.

### Other two models

Using length at birth and gestational age as predictors (main effects only)
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight)
```
Using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)
```
### Comparison
Make comparison in terms of the cross-validated prediction error between the models
```{r}
cv = crossv_mc(birthweight, 100) %>% 
  mutate(
    model_1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3 = map(train, ~lm(bwt ~ bhead + blength + babysex + 
               bhead * blength + bhead * babysex + blength * babysex + 
               bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))
    )

```
### The plot for RMSE
```{r}
cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin(color = "yellow") + 
  geom_boxplot(alpha = 0.5, color = "blue")
  
```
Base on the plot above, we can draw a conclusion that model 1 has the lowest RMSE, which means it is the best fitted model. The model 2 has the highest RMSE with the fewest predictors which performs the worst.

# Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Bookstrapping
```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = TRUE)
}

bootstrap_df = 
  tibble(
    strap_number = c(1:5000),
    strap_sample = rerun(5000, boot_sample(weather_df))
  )

weather_strap_results = bootstrap_df %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  )
```
### Adjusted R squared
```{r}
adj_r2 = 
  weather_strap_results %>%
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number, adj.r.squared)
  
  
adj_r2 %>%
  ggplot(aes(x = adj.r.squared)) +
  geom_density() +
  labs(
        title = "Distribution of R Squared",
        x = "Estimated R Squared") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
quantile(adj_r2 %>% pull(adj.r.squared), prob = c(0.025, 0.975))
```
The R-squared values by using bootstraping approximately follows a normal distribution with mean a little higher than 0.91, and the 95% confidence interval is [0.894, 0.927].

### Estimated log(beta0_hat * beta1_hat)

```{r}
log = 
  bootstrap_df %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(names_from = term, 
              values_from = estimate) %>% 
  janitor::clean_names() %>% 
  mutate(log = log(intercept * tmin))


log %>% 
  ggplot(aes(x = log)) +
  geom_density() +
  labs(
        title = "Distribution of Log(beta0_hat * beta1_hat)",
        x = "Estimated (beta0_hat * beta1_hat)")
```

```{r}
quantile(log %>% pull(log), prob = c(0.025, 0.975))
```
The values of log(beta0_hat * beta1_hat) by using bootstraping are approximately normally distributed with a mean around 2.02, and has a slightly longer tail on the left. The 95% confidence interval is [1.966, 2.059].
